Testing the precision of Bangla Communication Scale: Item Response Theory Guided Analysis

### 2022-03-08 communication.Rmd
TIFF and 600 dpi

corplot <- corplot <- ggcorrplot::ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", legend.title = "Correlation",
           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 6),
         axis.text.y = element_text(size = 6),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1),
         legend.text = element_text(size = 6),
         legend.title= element_text(size = 6))
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
ggsave("Figures/corplot.png",corplot, width = 3.5, height = 3.5, dpi = 600, bg ="white")

@@

knitr::include_graphics('Figures/corplot.png', dpi =600)

@@

factor <- cowplot::plot_grid(scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=2, 
                  align = "h", 
                  label_fontfamily = "sans",
                  label_fontface = "plain")
ggsave("Figures/factors.png",factor, width = 7, height = 3.5, dpi = 600)
```

@@

knitr::include_graphics("Figures/factors.png", dpi =600)

@@

#### Bangla Rotter's I-E Scale

To confirm the latent structure of Bangla Communication scale, we used the one factor solution with 17 items obtained in our Study 1.

@@

png(filename="Figures/CFAplot.png", 
    type="cairo",
    units="in", 
    width=3.5, 
    height=3.5, 
    pointsize=12, 
    res=600)
semPaths (fit.1 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="OpenMx",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          #exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1.2, #Font of factor and item name
          residuals=FALSE,
           #exoVar=FALSE,
          #fixedStyle=6, #Style of arrow (guide item)
          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

knitr::include_graphics("Figures/CFAplot.png", dpi =600)

@@

ggsave("Figures/personfit.jpeg",person , width = 3.5, height = 3.5, dpi = 600, bg = "white")

@@

ggsave("Figures/person.png",person , width = 3.5, height = 3.5, dpi = 600, bg = "white")

@@

```{r person-fit, fig.cap="Person Fit"}
knitr::include_graphics('Figures/personfit.jpeg')

@@

item11 <- ggicc(fit,7,6)+apatheme+ggtitle("item11")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
ggsave("Figures/ideal_icc.png",item11 , width = 12, height = 8, dpi = 600, bg = "white")

@@

ggsave("Figures/ICC.png",ICC , width = 7, height =7, dpi = 600, bg = "white")

@@

knitr::include_graphics("Figures/ICC.png", dpi =600)

@@

test.info <- tabledown::ggtestinfo(irt.data.1, fit)+ apatheme+geom_line(colour = "black", size=1.5)+geom_area(fill ="#E64B3599" )
# +geom_vline(xintercept = -3, colour ="black")+
#   geom_vline(xintercept = .5, colour ="black")
ggsave("Figures/TIC.png",test.info , width = 3.5, height = 3.5, dpi = 600, bg = "white")

@@

```{r saveWrightmao,  warning=F, message=F}
jpeg("Figures/personmap.jpeg", width = 7, height = 7, quality = 100,units="in", res= 1080, pointsize = 12 )
library(WrightMap)
WrightMap::wrightMap(estimation, threshold , 
          item.prop = 0.65,
          main.title = "Person-Map",
          # dim.names = c("Victimization", "Aggression"),
          thr.sym.col.fg = itemlevelcolors,
          thr.sym.col.bg = itemlevelcolors,
          vertLines = TRUE,
          show.thr.lab = F,
          dim.color = brewer.pal(5, "Set3"),
          label.items.srt = 45,
          cex = 1.5,
          return.thresholds=F
          )
```

@@

knitr::include_graphics('Figures/personmap.jpeg')

@@

ggsave("Figures/itemInfoplot.png",item.info.plot, width = 7, height =7, dpi = 600, bg ="white")

@@

```{r conrel-print, include=F}
##
png(filename="Figures/conrel.png", 
    type="cairo",
    units="in", 
    width=3.5, 
    height=3.5, 
    pointsize=12, 
    res=600)
library(latticeExtra)
library(directlabels)
font.settings <- list(
  font = 1,
  cex = 6,
  fontfamily = "sans")

@@

 plot(fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="Conditional Reliability Plot", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5 )

@@

knitr::include_graphics("Figures/itemInfoplot.png", dpi =600)

@@

```{r figTIC, fig.cap = "TIC.",  out.height='100%', warning=FALSE}
knitr::include_graphics("Figures/TIC.png", dpi =600)

@@

knitr::include_graphics("Figures/conrel.png", dpi =600)

>>>>

p.mat <- correlation::cor_to_p(correlations$rho, 428, method = "polychoric")

corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.8,
                      # insig = "blank",
           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 8),
         axis.text.y = element_text(size = 8),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))

ggsave("Figures/tiff/corplot.tiff",corplot, width = 3.5, height = 3.5, dpi = 600, compression = "lzw", bg ="White" )
ggsave("Figures/600/corplot.pdf",corplot, width = 3.5, height = 3.5, dpi = 600, bg ="White" )

@@

knitr::include_graphics('Figures/tiff/corplot.tiff', dpi =600)

@@

factor <- cowplot::plot_grid(scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=2, 
                  align = "h", 
                  label_fontfamily = "sans",
                  label_fontface = "plain")
ggsave("Figures/600/factors.png",factor, width = 7, height = 3.5, dpi = 600)

ggsave("Figures/tiff/factors.tiff",factor, width = 7, height = 3.5, dpi = 600)
```

@@

knitr::include_graphics("Figures/tiff/factors.tiff", dpi =600)

@@

@@

tiff(filename="Figures/tiff/CFAplot.tiff", 
    type="cairo",
    units="in", 
    width=3.5, 
    height=3.5, 
    pointsize=12, 
    res=600)
semPaths (fit.1 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="OpenMx",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          #exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1.2, #Font of factor and item name
          residuals=FALSE,
           #exoVar=FALSE,
          #fixedStyle=6, #Style of arrow (guide item)
          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

knitr::include_graphics("Figures/tiff/CFAplot.tiff", dpi =600)

@@

@@

ggsave("Figures/600/person.png",person , width = 3.5, height = 3.5, dpi = 600, bg = "white")

ggsave("Figures/tiff/person.tiff",person , width = 3.5, height = 3.5, dpi = 600, bg = "white")

@@

```{r person-fit, fig.cap="Person Fit"}
knitr::include_graphics('Figures/tiff/person.tiff')

@@

item11 <- ggicc(fit,7,6)+apatheme+ggtitle("item11")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
ggsave("Figures/600/ideal_icc.png",item11 , width = 12, height = 8, dpi = 600, bg = "white")

@@

ggsave("Figures/600/ICC.png",ICC , width = 7, height =7, dpi = 600, bg = "white")

ggsave("Figures/tiff/ICC.tiff",ICC , width = 7, height =7, dpi = 600, bg = "white")

@@

knitr::include_graphics("Figures/tiff/ICC.tiff", dpi =600)

@@

test.info <- tabledown::ggtestinfo(irt.data.1, fit)+ apatheme+geom_line(colour = "black", size=1.5)+geom_area(fill ="#E64B3599" )
# +geom_vline(xintercept = -3, colour ="black")+
#   geom_vline(xintercept = .5, colour ="black")
ggsave("Figures/600/TIC.png",test.info , width = 3.5, height = 3.5, dpi = 600, bg = "white")

ggsave("Figures/tiff/TIC.tiff",test.info , width = 3.5, height = 3.5, dpi = 600, bg = "white")

@@

```{r saveWrightmao,  warning=F, message=F}
tiff("Figures/tiff/personmap.tiff", width = 7, height = 7,units="in", res= 600, pointsize = 12 )
library(WrightMap)
WrightMap::wrightMap(estimation, threshold , 
          item.prop = 0.65,
          main.title = "Person-Map",
          # dim.names = c("Victimization", "Aggression"),
          thr.sym.col.fg = itemlevelcolors,
          thr.sym.col.bg = itemlevelcolors,
          vertLines = TRUE,
          show.thr.lab = F,
          dim.color = brewer.pal(5, "Set3"),
          label.items.srt = 45,
          cex = 1.5,
          return.thresholds=F
          )
```

@@

knitr::include_graphics('Figures/tiff/personmap.tiff')

@@

ggsave("Figures/600/itemInfoplot.png",item.info.plot, width = 7, height =7, dpi = 600, bg ="white")

ggsave("Figures/tiff/itemInfoplot.tiff",item.info.plot, width = 7, height =7, dpi = 600, bg ="white")

@@

```{r conrel-print, include=F}
##
tiff(filename="Figures/tiff/conrel.tiff", 
    type="cairo",
    units="in", 
    width=3.5, 
    height=3.5, 
    pointsize=12, 
    res=600)
library(latticeExtra)
library(directlabels)
font.settings <- list(
  font = 1,
  cex = 6,
  fontfamily = "sans")

@@

 plot(fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5 )

@@

knitr::include_graphics("Figures/tiff/itemInfoplot.tiff", dpi =600)

@@

```{r figTIC, fig.cap = "TIC.",  out.height='100%', warning=FALSE}
knitr::include_graphics("Figures/tiff/TIC.tiff", dpi =600)

@@

knitr::include_graphics("Figures/tiff/conrel.tiff", dpi =600)
